Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

@@

@@

>>>>

Finally, it is worth mentioning that $\Omega(n \log n)$ is a lower bound on the runtime of any comparison-based algorithm solving the $k$-SJ problem, even for $k = 2$. This can be established via a simple reduction (presented in Appendix~\ref{app:lb} for self-containment) from the {\em element distinctness} (ED) problem, where we are given $n$ real values $e_1, e_2, ..., e_n$ and need to decide whether there are distinct $i, j \in [n]$ satisfying $e_i = e_j$. The ED problem demands $\Omega(n \log n)$ comparisons to solve \cite{dl79}.

@@

In this paper, we show that the $k$-SJ problem can be settled by a comparison-based algorithm

@@

\appendix

\section{An $\bm{\Omega(n \log n)}$ Lower Bound} \label{app:lb}
